Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)

### 2014-02-14 MHCpaper/MHCsupp.tex
page numbering
updated MHC supp and slides

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\setcounter{tablerow}{0}\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
%
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
%\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^{\mathrm{b}-/-}$}
\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{A saturation model for impaired learning with enhanced plasticity: Supplementary material}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}

@@

\maketitle

@@

\tableofcontents
\listoffigures

@@

The values used for all these parameters in simulations are listed in \autoref{tab:params}.

\begin{figure}
 \begin{center}
 \parbox{0.8\linewidth}{%
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\hspace{0.5cm}\\[1cm]
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}
 \end{myenuma}
 }
 \end{center}
  \caption[Transition probabilities for different models]{Transition probabilities for different models.
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised X
  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  } \label{fig:models}
\end{figure}

@@

\begin{figure}
 \begin{center}
  \aligntop{\includegraphics[height=4cm]{pooled.svg}}
 \end{center}
  \caption[The pooled resource model]{The pooled resource model.
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.} \label{fig:pooled_model}
\end{figure}

@@

\begin{figure}
 \begin{center}
  \aligntop{\includegraphics[height=3cm]{multistate_nonuni.svg}}
 \end{center}
  \caption[The non-uniform multistate model]{The non-uniform multistate model.
  Similar to the multistate model, \autoref{fig:models}\ref{fig:multistate_model}), the synaptic weight varies linearly in the interval $[-1,1]$, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.} \label{fig:nonuni_model}
\end{figure}

@@

The features of the actual experiments that we'd like to capture are:
\begin{enumerate}
  \item Without pre-training, gain-increase learning is significantly faster in the wild-type than in the \KO\ mice.
  \item For the wild-type, gain-increase learning is significantly faster without pre-training than with it.
  \item For the \KO\ mice, gain-increase learning is significantly faster with pre-training than without it.
  \item After pre-training, gain-increase learning is significantly faster in the \KO\ mice than in the wild-type.
  \item Gain-decrease pre-training is slightly faster in the wild-type, but not significantly so.\label{it:gaindown}
\end{enumerate}
These questions will not be affected by any output nonlinearity, as long as it is monotonic and fixed.
We will not worry too much about \autoref{it:gaindown}, as gain-decrease learning uses a different mechanism to gain-increase.
We are only modelling the effect of gain-decrease training on \emph{these} synapses.

We will not worry too much about the curvature of the learning curves, as this can be changed by the nonlinear relation between synaptic weight and VOR gain.
However, both the wild-type and \KO\ mice should be affected in the same way, so the difference in the curvature of the \KO\ mice and wild-type curves after pre-training would be nice to capture.

@@

The values for all parameters we will use can be found in \autoref{tab:params}.

\begin{table}
 \begin{center}
  \begin{tabularn}{|l|c|c|c|c|c|c|}
    \cline{1-7}
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot & WT dep & \KO\ dep & $\Delta f$ & $r\tpre$ \\
    \cline{1-7}
    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.1  & 20  &\label{tr:multistate_weak} \\
    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.3  & 20  &\label{tr:multistate_med} \\
    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.45 & 30  &\label{tr:multistate_strong} \\
    Two-state     & 2  & $q=0.1$  & $q=0.1$  & $q=0.2$  & 0.1  & 5   &\label{tr:binary} \\
    Multistate    & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.3  & 5   &\label{tr:multistate_lin} \\
%    Pooled        & 10 & $q\in[0.3,0.4]$  & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
%                                          & 0.1 & 20 &\label{tr:pooled_plenty}\\
%    Pooled        & 10 & $q\in[0.05,0.4]$ & $q\in[0.05,0.4]$  & $q\in[0.1,0.8]$
%                                          & 0.1 & 20 &\label{tr:pooled_scarce}\\
    Pooled res. & 7  & $q=0.008$        & $q\in[0.0006,0.6]$  & $q\in[0.001,1]$
                                          & 0.4 & 20 &\label{tr:pooled_deponly}\\
    Cascade       & 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 20  &\label{tr:cascade_short} \\
    Cascade       & 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 100 &\label{tr:cascade_long} \\
    Non-uni. MS& 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 150 &\label{tr:nonuni} \\
    \cline{1-7}
%   \hline
%    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
%    & Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
%    \cline{1-7}
%    \label{tr:cascade_short}&
%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50   \\
%    \label{tr:cascade_long}&
%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150  \\
%    \label{tr:multistate_weak}&
%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50   \\
%    \label{tr:multistate_strong}&
%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20   \\
%    \label{tr:binary}&
%    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5  & 5    \\
%    \label{tr:pooled_plenty}&
%    Pooled     & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
%                                          & -0.1 & 70 & 70 \\
%    \label{tr:pooled_scarce}&
%    Pooled     & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
%                                          & -0.1 & 70 & 70 \\
%    \cline{1-7}
  \end{tabularn}
 \end{center}
  \caption{Parameters used in simulations.} \label{tab:params}
\end{table}

\newcommand{\arrangefig}[1]{\begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#1_learn.eps}}\label{fig:#1_learn}
  \item\aligntop{\includegraphics[width=7cm]{#1_learnS.eps}}\label{fig:#1_learnS}
  \\ \vp\vp
  \item\label{fig:#1_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_WT.eps}}\label{fig:#1_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_KO.eps}}\label{fig:#1_eq_KO}
                  \end{myenumi}
  \\ \vp \vp
  \item\label{fig:#1_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_nopre.eps}}\label{fig:#1_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_pre.eps}}\label{fig:#1_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_nopre.eps}}\label{fig:#1_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_pre.eps}}\label{fig:#1_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}}

\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ models with and without pre-training.
  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ models,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre},\ref{fig:#1_pr_KO_pre}) \KO\ models without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. }

\newcommand{\captionstart}[2]{Simulation results for the \textbf{#1} model with #2}
\newcommand{\captionstarts}[2]{Simulation results for the #1 model with #2}
\newcommand{\captionstartn}[1]{Simulation results for the \textbf{#1} model}
\newcommand{\captionstartsn}[1]{Simulation results for the #1 model}

\newcommand{\resultsfig}[4]{\begin{figure}
  \arrangefig{#4}
  \caption[\captionstarts{#1}{#2}]{\captionstart{#1}{#2 #3}.
  Other parameters \captiontext{#4} } \label{fig:#4}
\end{figure}}

\newcommand{\resultsfign}[2]{\begin{figure}
  \arrangefig{#2}
  \caption[\captionstartsn{#1}]{\captionstartn{#1}.
  Parameters \captiontext{#2} } \label{fig:#2}
\end{figure}}

@@

\resultsfig{serial}{weak training}{($\Delta f=0.1$)}{multistate_weak}

\resultsfig{serial}{moderate training}{($\Delta f=0.3$)}{multistate_med}

\resultsfig{serial}{strong training}{($\Delta f=0.45$)}{multistate_strong}

The results of simulations of the serial model can be seen in \autoref{fig:multistate_weak}, \autoref{fig:multistate_med} and \autoref{fig:multistate_strong}.
However, we can get some insight into this model analytically.

@@

First, consider the wild-type, for which $q\pot=q\dep=q$.
Without pre-training:
%
\begin{equation}\label{eq:multiWTnopre}
  \Phi = \frac{2{\Delta f}q}{M}.
\end{equation}
%
%where it's worth remembering that $\Delta f<0$.
With pre-training:
%
\begin{equation}\label{eq:multiWTpre}
\begin{aligned}
  \Phi &= 16(\Delta f)^2q \, \frac{(1+2\Delta f)^{M/2-1} (1-2\Delta f)^{M/2-1}}
          {(1+2\Delta f)^M - (1-2\Delta f)^M} \\
       &= \frac{4{\Delta f}\,q}{M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%
So, we see that pre-training will speed up learning when $\Delta f$ is small (in absolute value), as seen in \autoref{fig:multistate_weak}\ref{fig:multistate_weak_learnS} (black curves).
On the other hand, if $\Delta f$ is close to $\half$, pre-training will initially slow down learning a lot due to the factor of $(1-2\Delta f)^{M/2-1}$, as seen in \autoref{fig:multistate_strong}\ref{fig:multistate_strong_learnS}.

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[12pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}[table]
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figureautorefname}{Supplementary Figure}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
%\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^{\mathrm{b}-/-}$}
\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 S#2}}
\captionsetup{labelformat=supp}

@@

\setcounter{page}{6}
\setcounter{figure}{5}
\maketitle

@@

%\tableofcontents
%\listoffigures

@@

The values used for all these parameters in simulations are listed in \autoref{fig:sim_results}\ref{tab:params}.

\begin{figure}[p]
 \begin{center}
 \parbox{0.8\linewidth}{%
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\hspace{0.5cm}\\[1cm]
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}
 \end{myenuma}
 }
 \end{center}
  \caption[Transition probabilities for different models]{Transition probabilities for different models.
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised X
  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  } \label{fig:models}
\end{figure}

@@

\begin{figure}[p]
 \begin{center}
  \aligntop{\includegraphics[height=4cm]{pooled.svg}}
 \end{center}
  \caption[The pooled resource model]{The pooled resource model.
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.} \label{fig:pooled_model}
\end{figure}

@@

\begin{figure}[p]
 \begin{center}
  \aligntop{\includegraphics[height=3cm]{multistate_nonuni.svg}}
 \end{center}
  \caption[The non-uniform multistate model]{The non-uniform multistate model.
  Similar to the multistate model, \autoref{fig:models}\ref{fig:multistate_model}), the synaptic weight varies linearly in the interval $[-1,1]$, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.} \label{fig:nonuni_model}
\end{figure}

@@

The features of the actual experiments that we'd like to capture are:
\begin{enumerate}
  \item Without pre-training, gain-increase learning is significantly faster in the wild-type than in the \KO\ mice.
  \item For the wild-type, gain-increase learning is significantly faster without pre-training than with it.
  \item For the \KO\ mice, gain-increase learning is significantly faster with pre-training than without it.
  \item After pre-training, gain-increase learning is significantly faster in the \KO\ mice than in the wild-type.
%  \item Gain-decrease pre-training is slightly faster in the wild-type, but not significantly so.\label{it:gaindown}
\end{enumerate}
These questions will not be affected by any output nonlinearity, as long as it is monotonic and fixed.
We will not study gain-decrease learning, as it uses a different mechanism to gain-increase.
We are only modelling the effect of gain-decrease training on \emph{these} synapses.
We will also not discuss the curvature of the learning curves, as this can be changed by the nonlinear relation between synaptic weight and VOR gain.
%However, both the wild-type and \KO\ mice should be affected in the same way, so the difference in the curvature of the \KO\ mice and wild-type curves after pre-training would be nice to capture.

@@

The learning curves resulting from these simulations can be found in \autoref{fig:sim_results}.
The values for all parameters we will use can be found in \autoref{fig:sim_results}\ref{tab:params}.

\begin{figure}[p]
\begin{myenuma}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l@{\hspace{0.05\linewidth}}l}
      \item\label{fig:seial_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{serial.svg}}
      &
      \item\label{fig:binary_sim}
      \hspace{0.05\linewidth}\aligntop{\includegraphics[width=0.125\linewidth]{binary.svg}}
      &
      \item\label{fig:multistate_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{multistate.svg}}
      \\[1.5cm]
      \aligntop{\includegraphics[width=0.3\linewidth]{multistate_med_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{binary_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{multistate_lin_learnS.eps}}
      \\[5.5cm]
      \item\label{fig:pooled_sim}
      \aligntop{\includegraphics[width=0.3\linewidth]{pooled_deponly.svg}}
      &
      \item\label{fig:cascade_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{cascade.svg}}
      &
      \item\label{fig:nonuni_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{multistate_nonuni.svg}}
      \\[2cm]
      \aligntop{\includegraphics[width=0.3\linewidth]{pooled_deponly_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{cascade_long_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{nonuni_learnS.eps}}
  \end{tabular}

  \vspace{1cm}\item\label{tab:params}\aligntop{
  \begin{tabularn}{|l|c|c|c|c|c|c|}
    \cline{1-7}
    Model & \# states & pot & WT dep & \KO\ dep & $\Delta f$ & $r\tpre$ \\
    \cline{1-7}
    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.3  & 20  &\label{tr:multistate_med} \\
    Two-state     & 2  & $q=0.1$  & $q=0.1$  & $q=0.2$  & 0.1  & 5   &\label{tr:binary} \\
    Multistate    & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.3  & 5   &\label{tr:multistate_lin} \\
    Pooled res. & 7  & $q=0.008$        & $q\in[0.0006,0.6]$  & $q\in[0.001,1]$
                                          & 0.4 & 20 &\label{tr:pooled_deponly}\\
    Cascade       & 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 100 &\label{tr:cascade_long} \\
    Non-uni. MS& 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 150 &\label{tr:nonuni} \\
    \cline{1-7}
  \end{tabularn}}
  \end{myenuma}
  \caption[Simulation results for various models]{(\ref{fig:seial_sim}-\ref{fig:nonuni_sim}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (solid) and after gain-decrease pre-training (dashed) for wild-type (black) and \KO\ (red) models. (\ref{tab:params}) Parameters used for simulations.}\label{fig:sim_results}
\end{figure}

%\begin{table}
% \begin{center}
%  \begin{tabularn}{|l|c|c|c|c|c|c|}
%    \cline{1-7}
%    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
%    Model & \# states & pot & WT dep & \KO\ dep & $\Delta f$ & $r\tpre$ \\
%    \cline{1-7}
%%    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.1  & 20  &\label{tr:multistate_weak} \\
%    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.3  & 20  &\label{tr:multistate_med} \\
%%    Serial        & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.45 & 30  &\label{tr:multistate_strong} \\
%    Two-state     & 2  & $q=0.1$  & $q=0.1$  & $q=0.2$  & 0.1  & 5   &\label{tr:binary} \\
%    Multistate    & 10 & $q=0.3$  & $q=0.3$  & $q=0.4$  & 0.3  & 5   &\label{tr:multistate_lin} \\
%%    Pooled        & 10 & $q\in[0.3,0.4]$  & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
%%                                          & 0.1 & 20 &\label{tr:pooled_plenty}\\
%%    Pooled        & 10 & $q\in[0.05,0.4]$ & $q\in[0.05,0.4]$  & $q\in[0.1,0.8]$
%%                                          & 0.1 & 20 &\label{tr:pooled_scarce}\\
%    Pooled res. & 7  & $q=0.008$        & $q\in[0.0006,0.6]$  & $q\in[0.001,1]$
%                                          & 0.4 & 20 &\label{tr:pooled_deponly}\\
%%    Cascade       & 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 20  &\label{tr:cascade_short} \\
%    Cascade       & 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 100 &\label{tr:cascade_long} \\
%    Non-uni. MS& 10 & $x=0.25$ & $x=0.25$ & $x=0.33$ & 0.3  & 150 &\label{tr:nonuni} \\
%    \cline{1-7}
%%   \hline
%%    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
%%    & Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
%%    \cline{1-7}
%%    \label{tr:cascade_short}&
%%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50   \\
%%    \label{tr:cascade_long}&
%%    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150  \\
%%    \label{tr:multistate_weak}&
%%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50   \\
%%    \label{tr:multistate_strong}&
%%    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20   \\
%%    \label{tr:binary}&
%%    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5  & 5    \\
%%    \label{tr:pooled_plenty}&
%%    Pooled     & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
%%                                          & -0.1 & 70 & 70 \\
%%    \label{tr:pooled_scarce}&
%%    Pooled     & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
%%                                          & -0.1 & 70 & 70 \\
%%    \cline{1-7}
%  \end{tabularn}
% \end{center}
%  \caption{Parameters used for simulations in \autoref{fig:sim_results}.} \label{tab:params}
%\end{table}

%\newcommand{\arrangefig}[1]{\begin{center}
% \begin{myenuma}
%  \item\aligntop{\includegraphics[width=7cm]{#1_learn.eps}}\label{fig:#1_learn}
%  \item\aligntop{\includegraphics[width=7cm]{#1_learnS.eps}}\label{fig:#1_learnS}
%  \\ \vp\vp
%  \item\label{fig:#1_eq}\begin{myenumi}
%                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_WT.eps}}\label{fig:#1_eq_WT}
%                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_KO.eps}}\label{fig:#1_eq_KO}
%                  \end{myenumi}
%  \\ \vp \vp
%  \item\label{fig:#1_pr}\begin{myenumi}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_nopre.eps}}\label{fig:#1_pr_WT_nopre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_pre.eps}}\label{fig:#1_pr_WT_pre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_nopre.eps}}\label{fig:#1_pr_KO_nopre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_pre.eps}}\label{fig:#1_pr_KO_pre}
%                  \end{myenumi}
% \end{myenuma}
% \end{center}}
%
%\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
%  Time is measured in units of $1/r$, the mean time between plasticity events.
%  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ models with and without pre-training.
%  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
%  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ models,
%  with states of weak synaptic strength to the left and strong states to the right.
%  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre},\ref{fig:#1_pr_KO_pre}) \KO\ models without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
%  with states of weak synaptic strength at the top and strong states underneath. }
%
%\newcommand{\captionstart}[2]{Simulation results for the \textbf{#1} model with #2}
%\newcommand{\captionstarts}[2]{Simulation results for the #1 model with #2}
%\newcommand{\captionstartn}[1]{Simulation results for the \textbf{#1} model}
%\newcommand{\captionstartsn}[1]{Simulation results for the #1 model}
%
%\newcommand{\resultsfig}[4]{\begin{figure}
%  \arrangefig{#4}
%  \caption[\captionstarts{#1}{#2}]{\captionstart{#1}{#2 #3}.
%  Other parameters \captiontext{#4} } \label{fig:#4}
%\end{figure}}
%
%\newcommand{\resultsfign}[2]{\begin{figure}
%  \arrangefig{#2}
%  \caption[\captionstartsn{#1}]{\captionstartn{#1}.
%  Parameters \captiontext{#2} } \label{fig:#2}
%\end{figure}}

@@

%\resultsfig{serial}{weak training}{($\Delta f=0.1$)}{multistate_weak}
%
%\resultsfig{serial}{moderate training}{($\Delta f=0.3$)}{multistate_med}
%
%\resultsfig{serial}{strong training}{($\Delta f=0.45$)}{multistate_strong}

The results of simulations of the serial model can be seen in 
\autoref{fig:sim_results}\ref{fig:seial_sim}.
%\autoref{fig:multistate_weak}, \autoref{fig:multistate_med} and \autoref{fig:multistate_strong}.
However, we can get some insight into this model analytically.

@@

First, consider the wild-type, for which $q\pot=q\dep=q$.
Without pre-training:
%
\begin{equation}\label{eq:multiWTnopre}
  \Phi = \frac{2{\Delta f}q}{M}.
\end{equation}
%
%where it's worth remembering that $\Delta f<0$.
With pre-training:
%
\begin{equation}\label{eq:multiWTpre}
\begin{aligned}
  \Phi &= 16(\Delta f)^2q \, \frac{(1+2\Delta f)^{M/2-1} (1-2\Delta f)^{M/2-1}}
          {(1+2\Delta f)^M - (1-2\Delta f)^M} \\
       &= \frac{4{\Delta f}\,q}{M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%
So, we see that pre-training will speed up learning when $\Delta f$ is small (in absolute value).
%, as seen in \autoref{fig:multistate_weak}\ref{fig:multistate_weak_learnS} (black curves).
On the other hand, if $\Delta f$ is close to $\half$, pre-training will initially slow down learning a lot due to the factor of $(1-2\Delta f)^{M/2-1}$.
%, as seen in \autoref{fig:multistate_strong}\ref{fig:multistate_strong_learnS}.

Intuitively, the flux depends on the slope of the distribution at the centre of the chain (with an offset due to the difference between $f\pot$ and $f\dep$).
Pre-training has two effects: it produces a slope in the right direction 
%(see \autoref{fig:multistate_weak}\ref{fig:multistate_weak_eq}, red trace)
, but it also reduces the distribution at the centre. 
%(see \autoref{fig:multistate_strong}\ref{fig:multistate_strong_eq}, red trace).
For small $\Delta f$, the first effect is stronger and learning speeds up.
For larger $\Delta f$, the second effect wins and learning slows down.
